Experiment 5: Calibration Figure

### 2022-09-25 group-a/E1-calibration-figure.Rmd
added calibration figs, example trials figs, other edits

---
title: "Experiment 3: Calibration Figure"
output: html_notebook
---

@@

```{r include=FALSE}
calibration_points <- matrix(c(
  c(10,50),
  c(50,50),
  c(90,50),
  c(25,25),
  c(25,75),
  c(75,25),
  c(75,75)
), ncol=2, byrow=T)

validation_points <- matrix(c(
  c(10,50),
  c(50,50),
  c(90,50)
), ncol=2, byrow=T)

@@

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 3. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

>>>>

---
title: "Experiment 1: Calibration Figure"
output: pdf
---

@@

```{r include=FALSE}
# calib: 
    # //top
    # [15, 2],
    # [85, 2],
    # //bottom
    # [15, 95],
    # [85, 95],
    # 
    # //inner top
    # [32.5, 26],
    # [67.5, 26],
    # //inner bottom
    # [32.5, 72.5],
    # [67.5, 72.5],
    # 
    # [50, 50]
calibration_points <- matrix(c(
  c(15,2),
  c(85,2),
  c(15,95),
  c(85,95),
  c(32.5,26),
  c(67.5,26),
  c(32.5,72.5),
  c(67.5,72.5),
  c(50,50)
), ncol=2, byrow=T)
# valid: 
#      [,1] [,2]
 # [1,] 15.0  2.0
 # [2,] 85.0  2.0
 # [3,] 15.0 95.0
 # [4,] 85.0 95.0
 # [5,] 22.5 26.0
 # [6,] 67.5 26.0
 # [7,] 22.5 72.5
 # [8,] 67.5 72.5
 # [9,] 50.0 50.0
validation_points <- matrix(c(
  c(15,2),
  c(85,2),
  c(15,95),
  c(85,95),
  c(22.5, 26),
  c(67.5, 26),
  c(22.5, 72.5),
  c(67.5, 72.5),
  c(50,50)
), ncol=2, byrow=T)

@@

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 1. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

### 2022-09-25 group-b/E2-analysis-replication.Rmd
added calibration figs, example trials figs, other edits

The proportion of looks across quadrants in the free-viewing condition was analyzed in linear mixed-effects model with quadrant as the predictor (critical as the reference level). The model included random intercepts and slopes for participants^[ `lme4` syntax: `lmer(proportion ~ quadrant + (1+quadrant|subject_id))`. Among other limitations, this approach violates the independence assumptions of the linear model because looks to the four locations are not independent. This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.] Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: _b_ =  `r E2_gaze_model_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 )

@@

```{r, eval = F}
acc.anova <- ezANOVA(acc.behavioral.subject.data, dv=accuracy, wid=subject_id, within = c(relation, condition))
acc.anova$ANOVA
```
*Q: Can we recover item IDs to do crossed random effects?*

>>>>

The proportions of looks across quadrants in the free-viewing condition were analyzed using a linear mixed-effects model with quadrant as the predictor (critical as the reference level). The model included random intercepts and slopes for participants^[ `lme4` syntax: `lmer(proportion ~ quadrant + (1+quadrant|subject_id))`. Among other limitations, this approach violates the independence assumptions of the linear model because looks to the four locations are not independent. This analysis was chosen because it is analogous to the ANOVA analysis conducted in the original paper.]. Proportions of looks were significantly higher for the critical quadrant compared to the other three (first: _b_ =  `r E2_gaze_model_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 )

@@

```{r, eval = F}
acc.anova <- ezANOVA(acc.behavioral.subject.data, dv=accuracy, wid=subject_id, within = c(relation, condition))
acc.anova$ANOVA
```

### 2022-09-25 group-c/E3-analysis-replication.Rmd
added calibration figs, example trials figs, other edits

```{r Plot of cumulative looking score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
  geom_pointrange()+
  labs(x = "Time (ms)", y = "Cumulative Looking Score")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

@@

```{r Plot Looking Score Correlations, echo=FALSE}
ggplot(looking.plus.behavioral %>% filter(rt_recognition < 10000), aes(x=looking.score, y=rt_recognition))+
  geom_point()+
  theme_bw()
```

>>>>

```{r plot-cumulative-looking-score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
  geom_pointrange()+
  labs(x = "Time (ms)", y = "Cumulative Looking Score")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

@@

```{r Plot Looking Score Correlations, echo=FALSE, warning=FALSE}
ggplot(looking.plus.behavioral %>% filter(rt_recognition < 10000), aes(x=looking.score, y=rt_recognition))+
  geom_point()+
  theme_bw()
```

### 2022-09-25 group-d/E4-calibration-figure.Rmd
added calibration figs, example trials figs, other edits

---
title: "Experiment 2: Calibration Figure"
output: html_notebook
---

@@

```{r include=FALSE}
# calib: [25,25],[25,75],[50,50],[75,25],[75,75]
calibration_points <- matrix(c(
  c(25,25),
  c(25,75),
  c(50,50),
  c(75,25),
  c(75,75)
), ncol=2, byrow=T)
# valid: c(25, 25, 50, 75, 75, 25, 75, 50, 25, 75)
#      [,1] [,2]
# [1,]   25   25
# [2,]   25   75
# [3,]   50   50
# [4,]   75   25
# [5,]   75   75
validation_points <- matrix(c(
  c(25,25),
  c(25,75),
  c(50,50),
  c(75,25),
  c(75,75)
), ncol=2, byrow=T)

@@

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 2. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

>>>>

---
title: "Experiment 4: Calibration Figure"
output: pdf
---

@@

```{r include=FALSE}
# calib: [25,25],[25,75],[50,50],[75,25],[75,75]
calibration_points <- matrix(c(
  c(25,25),
  c(25,75),
  c(50,50),
  c(75,25),
  c(75,75)
), ncol=2, byrow=T)
# valid: 
#     [,1] [,2]
# [1,]   25   25
# [2,]   25   75
# [3,]   50   50
# [4,]   75   25
# [5,]   75   75
validation_points <- matrix(c(
  c(25,25),
  c(25,75),
  c(50,50),
  c(75,25),
  c(75,75)
), ncol=2, byrow=T)

@@

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 4. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

### 2022-09-25 group-e/E5-calibration-figure.Rmd
added calibration figs, example trials figs, other edits

---
title: "Experiment 1: Calibration Figure"
output: pdf
---

@@

```{r include=FALSE}
# calib: 
    # //top
    # [15, 2],
    # [85, 2],
    # //bottom
    # [15, 95],
    # [85, 95],
    # 
    # //inner top
    # [32.5, 26],
    # [67.5, 26],
    # //inner bottom
    # [32.5, 72.5],
    # [67.5, 72.5],
    # 
    # [50, 50]
calibration_points <- matrix(c(
  c(15,2),
  c(85,2),
  c(15,95),
  c(85,95),
  c(32.5,26),
  c(67.5,26),
  c(32.5,72.5),
  c(67.5,72.5),
  c(50,50)
), ncol=2, byrow=T)
# valid: 
#      [,1] [,2]
 # [1,] 15.0  2.0
 # [2,] 85.0  2.0
 # [3,] 15.0 95.0
 # [4,] 85.0 95.0
 # [5,] 22.5 26.0
 # [6,] 67.5 26.0
 # [7,] 22.5 72.5
 # [8,] 67.5 72.5
 # [9,] 50.0 50.0
validation_points <- matrix(c(
  c(15,2),
  c(85,2),
  c(15,95),
  c(85,95),
  c(22.5, 26),
  c(67.5, 26),
  c(22.5, 72.5),
  c(67.5, 72.5),
  c(50,50)
), ncol=2, byrow=T)

@@

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 1. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

>>>>

---
title: "Experiment 5: Calibration Figure"
output: pdf
---

@@

```{r include=FALSE}
# calib: [25,25],[25,75],[50,50],[75,25],[75,75],[25,50],[75,50],[15,50],[85,50]
calibration_points <- matrix(c(
  c(25,25),
  c(25,75),
  c(50,50),
  c(75,25),
  c(75,75),
  c(25,50),
  c(75,50),
  c(15,50),
  c(85,50)
), ncol=2, byrow=T)
# valid: 
#      [,1] [,2]
# [1,]   25   50
# [2,]   75   50
# [3,]   50   50
validation_points <- matrix(c(
  c(25,50),
  c(75,50),
  c(50,50)
), ncol=2, byrow=T)

@@

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 5. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```
